Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex

>>>>

\begin{figure}
\includegraphics{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}
